A Technique for Inter-Catalogue Recommendations

### 2014-06-10 paper2/paper.tex
Small edits

\section*{Constructing Recommendations}
Recommending products between different catalogues is a daunting task.
Traditionally, constructing recommendations is done by leveraging user behavior
using a collaborative filtering technique. At the most basic level, If a large
number of users view or purchase both Product A and Product B, the two are
connected with a recommendation. Unfortunately, for this problem there are no
user data between the two unconnected catalogues.

\subsection*{Content Based Similarity}
A simple approach for this problem is to recommend products that have similar
content. The products have both a short and long description which we can use to
construct a textual content-based similarity function. To do this, we represent each
product as a vector of tf-idf values for each word in its descriptions. By using
tf-idf, we reduce the relevance of frequent words and boost that of rare ones,
thus emphasizing the more words that are more descriptive of a product versus
all the other ones in the catalogue. The vector representations are the length 
of the dictionary, with zeros for all words not in the descriptions. To determine
the content-based similarity between two products, we simply take the dot 
product of the two tf-idf vectors.

Mathematical definition of content-based similairty...

This similarity function yields the following recommendation algorithm: For each
product, scan through the products in the opposite catalogue and calculate the
content-based similarity score with each. Predict recommendations between this
product and each of the top k most similar products in the other catalogue.

While this is a quadric-time operation, it can be sped up using matrix
multiplication. Furthermore, the division into different categories reduces the
impact of the quadratic effect. For instance, Macy's entire catalogue consists
of over ONE MILLION products, making a quadratic time algorithm infeasible.
However, the average category has 2000 products, which is significantly more
manageable.

\subsection*{Leveraging Recommendations}
The simple content-based recommender is limited for a few reasons. It attempts
to capture similarity between products by looking exclusively at the words used
to describe them. One limitation here is that different brands often use
different vocabularies to describe the same thing, such as ``off-white'' versus
``ivory.'' Another issue is that the best recommendation for a product is often
more subtle than simply the most similar other product. For instance, a striped
black-and-white button-up shirt may be an excellent recommendation for a blue
checkered button-up, even though the two have ostensibly different patterns and
colors.

>>>>

\section*{Constructing Recommendations}
Recommending products between different catalogues is a difficult task.
Typically, recommendations are constructed by leveraging user behavior
with a collaborative filtering technique. At the most basic level, If a large
number of users view or purchase both Product A and Product B, the two products
are recommended for each other. Unfortunately, for this problem there are no
user data between the two unconnected catalogues.

\subsection*{Content Based Similarity}
A simple approach is to recommend products that have similar content. Each product
has includes a short description which we can use to construct a textual 
content-based similarity function. To do this, we represent each
product as a vector of tf-idf values for each word in its descriptions. By using
tf-idf, we reduce the relevance of frequent words and boost that of rare ones.
This emphasizes the words that better explain this product versus all the other 
ones in the catalogue. The vector representations are the length of the
vocabulary. They are very sparse as most words do not appear in any given
product description. With this tf-idf represenation, we can define the 
$ContentSimiarity$ functoin as follows:

\begin{align}
ContentSimilarity(P_1, P_2) &= v_1 \cdot v_2
\end{align}
where $P_1$ and $P_2$ are the products being compared and $v_1$ and $v_2$ are
their representations as tf-idf vectors.

This similarity function yields the following recommendation algorithm which we
call the $ContentBased Recommender$: For each
product, scan through the products in the opposite catalogue and calculate the
content-based similarity score with each. Predict recommendations between this
product and each of the top k most similar products in the other catalogue.

While this is a quadric-time operation, it can be sped up using matrix
multiplication. Furthermore, the division into different categories reduces the
impact of the quadratic effect. In our case, Macy's entire catalogue consists
of over $60,000$ products, making a quadratic time algorithm very slow.
However, the average category has only one or two thousand products, which is 
significantly more manageable size for quadratic operations.

\subsection*{Leveraging Recommendations}
This $ContentBased Recommender$ is limited in a few ways. For one, it attempts
to capture similarity between products by looking exclusively at the words used
to describe them. One limitation here is that different brands often use
different vocabularies to describe the same thing, such as ``off-white'' versus
``ivory.'' Another issue is that the best recommendation for a product is often
more subtle than simply the most similar other product. For instance, a striped
black-and-white button-up shirt may be an excellent recommendation for a blue
checkered button-up, even though the two have ostensibly different patterns and
colors.
